---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slopeflex

The goal of `slopeflex` is to estimate change points (slope flexes) for a vector of daily time series data including any future not-yet-observed slope flexes/changes/shifts.

Both instances require a prior on what the slope flex/shift/change is going to be. When data are available for a given point, the model estimates the change accordingly. When data are not available, the model will forecast accordingly using the provided prior.

This package is useful when dates anytime dates for existing change points (slope flexes) are known. It is likewise informative for modeling future change points.

## Installation

You can install the development version of slopeflex from Github:

``` r
install.packages('remotes')
remotes::install_github("dantonnoriega/slopeflex")
```

## Example

Here is an example of how slopeflex works using simulated data.

```{r example, code=xfun::read_utf8('dev/XB-test.R')}
```